A global sensitivity analysis of wind turbine aeroelastic models

### 2019-11-25 Paper/article.tex
added more references to appendix in paper

\section*{Acknowledgements}
\bibliography{\myreferences}

\appendix
\section{Literature overview}
List of BEM codes in \cite{Sayed2019,Vorpahl2013}.

@@

>>>>

\section*{Acknowledgements}

\newpage

\section{References}
\bibliography{\myreferences}

\newpage

\appendix
\section{Literature overview of global sensitivity analysis in wind-turbine models}
List of BEM codes in \cite{Sayed2019,Vorpahl2013}.

@@

\cite{Fluck2018} develop an \textit{intrusive} stochastic BEM method: `a stochastic solution for the unsteady aerodynamic loads based on a projection of the unsteady Blade Element Momentum (BEM) equations onto a stochastic space spanned by chaos exponentials'.

\cite{Hubler2017} used global sensitivity analysis (as part of a four-step approach) to reduce the parameter dimension for structural behaviour computations using FAST as aeroelastic code. The methods of expert knowledge, one-at-a-time variation, and regression based on Monte Carlo sampling are used as pre-processing steps to reduce the computational expense of global sensitivity analysis.
